MS Prelim Data K23, using Depression T=3.09 mask

### 2022-08-13 K23_prelim_data_using_dep_T_3_09_mask_20220630.Rmd
Add files via upload

@@

    *MS disease and depression network overlap:
      - Ms disease within depression network (31%) versus outside (14%), p < 2.2* 10^-16
      - MS disease within depression 10% network (30%) versus outside (14%), p < 2.2 * 10^-16
      - MS disease within depression 5% network (30%) versus outside (14%), p < 2.2 * 10^-16
      - Linear Regressions (essentially matching t tests above): 
         +depressed v healthy within dep network in (p = 0.055); 
         +dep vs healthy within dep 10% (p = 0.053);
         +dep vs healthy within non dep network (p = 0.042)
      - Take home: Multiple sclerosis white matter lesions co-locate with brain regions previously associated with depression, irrespective of diagnosis. Suggests a final possible common pathway? Shared biology? This may also in part explain why rates of depression in MS are much higher than rates of depression in other autoimmune conditions. 
    *Depression by individual fascicle:
      - Nothing corrects at this time, unfortunately. 
      - P<0.05, uncorrected findings:
          -AF_R	0.03235420			
          -FAT_R	0.03337075			
          -SLF2_R	0.04066933			
          -CPT_F_R	0.04932598			
          -CPT_O_L	0.04346334			
          -CPT_P_R	0.03471933			
          -DRTT_R	0.01914199			
          -ML_R	0.01259474			
          -TR_S_R	0.01724321	
    Fascicle loss x PHQ9:
     - Nothing significant by individual fascicle, within association network, by fascicle within the depression network
     - similarly, no significant findings looks at means of all fascicle loss, within dep network, 10% and 5% and non-depression network

@@

#write.table(fascicle_names,"/Users/eballer/BBL/msdepression/templates/dti/HCP_YA1065_tractography/fascicle_names.csv", row.names = F, quote = F, col.names = F)

@@

@@

a<-ggplot(data = fascicle_volumes_dep, aes(x = fascicle, y=prop_in_mask), main = "Proportion of Volume per Fascicle Affected Dep net 3_09") + 
  geom_bar(stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
print(a)

@@

plot_all_fascicles_r_and_l_sep <-ggplot(data = fascicle_values_dep_sorted_by_overlap, aes(x = fascicle, y=prop_in_mask), main = "Proportion of Volume per Fascicle Affected Dep net 3_09") + 
  geom_bar(stat="identity") +
  ylim(0,0.4) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
print(plot_all_fascicles_r_and_l_sep)

#get top quartile
quartile <- round((dim(fascicle_values_dep_sorted_by_overlap)[1] / 4),0)
dep_network_names_top_quartile<- (fascicle_values_dep_sorted_by_overlap[order(fascicle_values_dep_sorted_by_overlap$prop_in_mask, decreasing = TRUE),])$fascicle[1:quartile]

@@

sorted_ggplot<-ggplot(data = fascicle_values_dep_sorted_by_overlap, aes(x = fascicle, y=prop_in_mask), main = "Proportion of Volume per Fascicle Affected Dep net 3_09") + 
  geom_bar(stat="identity") +
  ylim(0,0.4) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
print(sorted_ggplot)

@@

@@

sorted_ggplot<-ggplot(data = fascicle_values_sorted_by_overlap, aes(x = fascicle, y=value), main = "Proportion of Volume per Fascicle Affected") + 
  geom_bar(stat="identity") +
  ylim(0,0.8) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
print(sorted_ggplot)

@@

sorted_ggplot_healthy<-ggplot(data = fascicle_values_sorted_by_overlap, aes(x = fascicle, y=value), main = "Proportion of Volume per Fascicle Affected in Non Depressed") + 
  geom_bar(stat="identity") +
  ylim(0,0.8) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
print(sorted_ggplot_healthy)

# ordered by mean value overall
fascicle_values_sorted_by_overlap$fascicle <- factor(fascicle_values_sorted_by_overlap$fascicle, levels = order_of_mean_values_overall)
sorted_ggplot_healthy_ordered<-ggplot(data = fascicle_values_sorted_by_overlap, aes(x = fascicle, y=value), main = "Proportion of Volume per Fascicle Affected Ordered by mean values NonDepressed") + 
  geom_bar(stat="identity") +
  ylim(0,0.8) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
print(sorted_ggplot_healthy_ordered)

@@

sorted_ggplot_depressed<-ggplot(data = fascicle_values_sorted_by_overlap, aes(x = fascicle, y=value), main = "Proportion of Volume per Fascicle Affected Depressed") + 
  geom_bar(stat="identity") +
  ylim(0,0.8) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
print(sorted_ggplot_depressed)

# ordered by mean value overall
fascicle_values_sorted_by_overlap$fascicle <- factor(fascicle_values_sorted_by_overlap$fascicle, levels = order_of_mean_values_overall)
sorted_ggplot_depressed_ordered<-ggplot(data = fascicle_values_sorted_by_overlap, aes(x = fascicle, y=value), main = "Proportion of Volume per Fascicle Affected Ordered by mean values Depressed") + 
  geom_bar(stat="identity") +
  ylim(0,0.8) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
print(sorted_ggplot_depressed_ordered)
```

>>>>

Depression top quartile, r&l separated
 [1] "SLF3_R"  "AF_R"    "AF_L"    "SLF2_R"  "CBT_R"   "FAT_R"   "CS_P_R"  "C_PHP_R" "MdLF_L"  "FAT_L"   "SLF2_L"  "MdLF_R"  "CBT_L"   "TR_P_L"  "TR_S_R" 
[16] "CPT_O_R" "TR_P_R"  "PAT_L"   "PAT_R"   "EMC_R"   "TR_S_L"  "CC"

Depression top quartile, r&l meaned
[1] AF    SLF3  SLF2  FAT   MdLF  CST   CPT_O PAT   C_PHP CS_A  CC    CPT_F

@@

    *MS disease and depression network overlap:
      - Ms disease within depression network (31%) versus outside (14%), p < 2.2* 10^-16
      - MS disease within depression 10% network (30%) versus outside (14%), p < 2.2 * 10^-16
      - MS disease within depression 5% network (30%) versus outside (14%), p < 2.2 * 10^-16
      - MS disease within depression top quartile network (31%) versus areas with no overlap (14%), p < 2.2 x 10^-16
      - MS disease within depression top quartile network (31%) versus outside depression top quartile network (24%), p 1.7 * 10^-5
      - Linear Regressions (essentially matching t tests above): 
         +depressed v healthy within dep network in (p = 0.055); 
         +dep vs healthy within dep 10% (p = 0.053);
         +dep vs healthy within non dep network (p = 0.042)
         +dep vs healthy within dep top quartile (p = 0.054);
      - Take home: Multiple sclerosis white matter lesions co-locate with brain regions previously associated with depression, irrespective of diagnosis. Suggests a final possible common pathway? Shared biology? This may also in part explain why rates of depression in MS are much higher than rates of depression in other autoimmune conditions. 
    *Depression by individual fascicle:
      - Nothing corrects at this time, unfortunately. 
      - P<0.05, uncorrected findings:
          -AF_R	0.03235420			
          -FAT_R	0.03337075			
          -SLF2_R	0.04066933			
          -CPT_F_R	0.04932598			
          -CPT_O_L	0.04346334			
          -CPT_P_R	0.03471933			
          -DRTT_R	0.01914199			
          -ML_R	0.01259474			
          -TR_S_R	0.01724321	
    Fascicle loss x PHQ9:
     - Nothing significant by individual fascicle, within association network, by fascicle within the depression network
     - similarly, no significant findings looks at means of all fascicle loss, within dep network, 10% and 5% and non-depression network

@@

#fascicle names are contained in all but the first 2 columns of the fascicle_proportions df
fascicle_names <- names(fascicle_proportions[3:dim(fascicle_proportions)[2]])
fascicle_names_no_cranial_nerves <- fascicle_names[grep("CN", fascicle_names, invert = TRUE)] #n=77
#write.table(fascicle_names,"/Users/eballer/BBL/msdepression/templates/dti/HCP_YA1065_tractography/fascicle_names.csv", row.names = F, quote = F, col.names = F)

@@

fascicle_names_dep_network_all_no_cranial_nerves <- fascicle_names_dep_network_all[grep("CN", fascicle_names_dep_network_all, invert = TRUE)]

@@

a<-ggplot(data = fascicle_volumes_dep, aes(x = fascicle, y=prop_in_mask), main = "Proportion of Volume per Fascicle Affected Dep net 3_09") + 
  geom_bar(stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        axis.text.y = element_text(size=2),
        plot.title = element_text(hjust = 0.5))
print(a)

@@

plot_all_fascicles_r_and_l_sep <-ggplot(data = fascicle_values_dep_sorted_by_overlap, aes(x = fascicle, y=prop_in_mask))+
  ggtitle("Proportion of Volume per Fascicle Affected Dep net 3_09") + 
  geom_bar(stat="identity") +
  ylab("Proportion in Depression Mask") +
  ylim(0,0.4) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(hjust = 0.5))
print(plot_all_fascicles_r_and_l_sep)

fascicles_r_and_l_sep_no_cranial_nerves <- fascicle_values_dep_sorted_by_overlap %>% filter(fascicle %in% fascicle_names_no_cranial_nerves)

plot_all_fascicles_r_and_l_sep_no_cranial_nerves <-ggplot(data = fascicles_r_and_l_sep_no_cranial_nerves, aes(x = fascicle, y=prop_in_mask))+
  ggtitle("Proportion of Volume Overlap per Fascicle 3_09") + 
  geom_bar(stat="identity") +
  xlab("Fascicle") +
  ylab("Overlap with Depression Mask") +
  ylim(0,0.4) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(hjust = 0.5, size=30),
        axis.title.x = element_text(size=30),
        axis.title.y = element_text(size=30))
print(plot_all_fascicles_r_and_l_sep_no_cranial_nerves)

#### get top quartile; 
#figure out how many fascicles that is, then 
quartile <- round((dim(fascicle_values_dep_sorted_by_overlap)[1] / 4),0)

#quartile <- floor((dim(fascicle_values_dep_sorted_by_overlap)[1] / 4))

#sort all the fascicles by %overlap, in decreasing order (so highest overlap at the top), and then take the top 1-quartile
dep_network_names_top_quartile_preproc<- (fascicle_values_dep_sorted_by_overlap[order(fascicle_values_dep_sorted_by_overlap$prop_in_mask, decreasing = TRUE),])$fascicle[1:quartile]

dep_network_names_bottom_quartile_preproc<- (fascicle_values_dep_sorted_by_overlap[order(fascicle_values_dep_sorted_by_overlap$prop_in_mask, decreasing = FALSE),])$fascicle[1:quartile]
#make sure it right format, character

dep_network_names_top_quartile <- as.character(dep_network_names_top_quartile_preproc)

#get a network that includes all of the fascicles NOT in dep 25% network
dep_network_bottom_3_quartiles <- fascicle_names[!(fascicle_names %in% dep_network_names_top_quartile_preproc)]
dep_network_names_bottom_quartile <- fascicle_names[(fascicle_names %in% dep_network_names_bottom_quartile_preproc)]

#plot values within the depression network, and values outside of it

fascicles_dep_25_percent_for_plot <- fascicle_values_dep_sorted_by_overlap[(fascicle_values_dep_sorted_by_overlap$fascicle %in% dep_network_names_top_quartile_preproc),]

plot_all_fascicles_r_and_l_sep_top_quartile <-ggplot(data = fascicles_dep_25_percent_for_plot, aes(x = fascicle, y=prop_in_mask))+
  ggtitle("Proportion of Volume per Fascicle Affected Dep net 3_09, top quartile") + 
  geom_bar(stat="identity") +
  ylab("Proportion in Depression Mask") +
  ylim(0,0.4) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(hjust = 0.5))
print(plot_all_fascicles_r_and_l_sep_top_quartile)

#bottom 3 quartiles
fascicles_dep_bottom_3_quartiles_for_plot <- fascicle_values_dep_sorted_by_overlap[(fascicle_values_dep_sorted_by_overlap$fascicle %in% dep_network_bottom_3_quartiles),]

plot_all_fascicles_r_and_l_sep_bottom_3_quartiles <-ggplot(data = fascicles_dep_bottom_3_quartiles_for_plot, aes(x = fascicle, y=prop_in_mask))+
  ggtitle("Proportion of Volume per Fascicle Affected Dep net 3_09, bottom 3 quartiles") + 
  geom_bar(stat="identity") +
  ylim(0,0.4) +
  ylab("Proportion in Depression Mask") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(hjust = 0.5))
print(plot_all_fascicles_r_and_l_sep_bottom_3_quartiles)

#plot values within the depression network, and values outside of it

fascicles_dep_bottom_quartile_for_plot <- fascicle_values_dep_sorted_by_overlap[(fascicle_values_dep_sorted_by_overlap$fascicle %in% dep_network_names_bottom_quartile_preproc),]

plot_all_fascicles_r_and_l_sep_bottom_quartile <-ggplot(data = fascicles_dep_bottom_quartile_for_plot, aes(x = fascicle, y=prop_in_mask)) +
  ggtitle("Proportion of Volume per Fascicle Affected Dep net 3_09, bottom quartile") + 
  geom_bar(stat="identity") +
  ylim(0,0.4) +
  ylab("Proportion in Depression Mask") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(hjust = 0.5))
print(plot_all_fascicles_r_and_l_sep_bottom_quartile)

##################
### Sensitivity analysis, repeat this all but exclude cranial nerves
##################

### remove all rows with cranial nerves in them
# of note, we do not have all cranial nerves represented, we only have, CNII (optic), III(oculomotor), V (trigeminal), VII(facial), VIII(vestibulocochlear)
fascicle_values_dep_no_cranial_nerves = fascicle_values_dep_sorted_by_overlap[(grep(pattern = "CN", x = fascicle_values_dep_sorted_by_overlap$fascicle, invert = TRUE)),]

#figure out how many fascicles that is, then 
quartile <- round((dim(fascicle_values_dep_no_cranial_nerves)[1] / 4),0)
#quartile <- floor((dim(fascicle_values_dep_no_cranial_nerves)[1] / 4))

#sort all the fascicles by %overlap, in decreasing order (so highest overlap at the top), and then take the top 1-quartile
dep_network_names_top_quartile_preproc_no_cranial_nerves<- (fascicle_values_dep_no_cranial_nerves[order(fascicle_values_dep_no_cranial_nerves$prop_in_mask, decreasing = TRUE),])$fascicle[1:quartile] #n=19

dep_network_names_bottom_quartile_preproc_no_cranial_nerves<- (fascicle_values_dep_sorted_by_overlap[order(fascicle_values_dep_no_cranial_nerves$prop_in_mask, decreasing = FALSE),])$fascicle[1:quartile]
#make sure it right format, character

#make sure it right format, character

dep_network_names_top_quartile_no_cranial_nerves <- as.character(dep_network_names_top_quartile_preproc_no_cranial_nerves) #n=19

#get a network that includes all of the fascicles NOT in dep 25% network
dep_network_bottom_3_quartiles_no_cranial_nerves <- fascicle_values_dep_no_cranial_nerves$fascicle[!(fascicle_values_dep_no_cranial_nerves$fascicle %in% dep_network_names_top_quartile_preproc_no_cranial_nerves)] #n=68

#bottom quartile
dep_network_names_bottom_quartile_no_cranial_nerves <- fascicle_names[(fascicle_names %in% dep_network_names_bottom_quartile_preproc_no_cranial_nerves)]

#get a network than includes all of the fascicles with NO overlap with depression network
nondep_network_names_no_cranial_nerves <- fascicle_values_dep_no_cranial_nerves$fascicle[fascicle_values_dep_no_cranial_nerves$prop_in_mask == 0] #n=15

#plot values within the depression network, and values outside of it

fascicles_dep_25_percent_for_plot_no_cranial_nerves <- fascicle_values_dep_sorted_by_overlap[(fascicle_values_dep_sorted_by_overlap$fascicle %in% dep_network_names_top_quartile_preproc_no_cranial_nerves),]

plot_all_fascicles_r_and_l_sep_top_quartile_no_cranial_nerves <-ggplot(data = fascicles_dep_25_percent_for_plot_no_cranial_nerves, aes(x = fascicle, y=prop_in_mask)) + 
  geom_bar(stat="identity") +
  ggtitle("Proportion of Volume per Fascicle Affected Dep net 3_09, top quartile") + 
  ylim(0,0.4) +
  ylab("Proportion in Depression Mask") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(hjust = 0.5, size=30),
        axis.title.x = element_text(size=30),
        axis.title.y = element_text(size=30))
print(plot_all_fascicles_r_and_l_sep_top_quartile_no_cranial_nerves)

#bottom 3 quartiles
fascicles_dep_bottom_3_quartiles_for_plot_no_cranial_nerves <- fascicle_values_dep_sorted_by_overlap[(fascicle_values_dep_sorted_by_overlap$fascicle %in% dep_network_bottom_3_quartiles_no_cranial_nerves),]

plot_all_fascicles_r_and_l_sep_bottom_3_quartiles_no_cranial_nerves <-ggplot(data = fascicles_dep_bottom_3_quartiles_for_plot_no_cranial_nerves, aes(x = fascicle, y=prop_in_mask)) + 
  geom_bar(stat="identity") +
  ylab("Proportion in Depression Mask") +
  ggtitle("Proportion of Volume per Fascicle Affected Dep net 3_09, bottom three quartiles") + 
  ylim(0,0.4) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(hjust = 0.5))
print(plot_all_fascicles_r_and_l_sep_bottom_3_quartiles_no_cranial_nerves) #n=58, which is total 68 - 10 CNs

#bottom quartile
fascicles_dep_bottom_quartile_for_plot_no_cranial_nerves <- fascicle_values_dep_sorted_by_overlap[(fascicle_values_dep_sorted_by_overlap$fascicle %in% dep_network_names_bottom_quartile_preproc_no_cranial_nerves),]

plot_all_fascicles_r_and_l_sep_bottom_quartile_no_cranial_nerves <-ggplot(data = fascicles_dep_bottom_quartile_for_plot_no_cranial_nerves, aes(x = fascicle, y=prop_in_mask), main = "Proportion of Volume per Fascicle Affected Dep net 3_09, bottom quartile") + 
  geom_bar(stat="identity") +
  ylab("Proportion in Depression Mask") +
  ggtitle("Proportion of Volume per Fascicle Affected Dep net 3_09, bottom quartile") + 
  ylim(0,0.4) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(hjust = 0.5))
print(plot_all_fascicles_r_and_l_sep_bottom_quartile_no_cranial_nerves)

#non dep network, no cranial nerves
nondep_network_for_plot_no_cranial_nerves <- fascicle_values_dep_sorted_by_overlap %>% filter(fascicle_values_dep_sorted_by_overlap$fascicle %in% nondep_network_names_no_cranial_nerves)

plot_all_fascicles_nondep_network_for_plot_no_cranial_nerves  <-ggplot(data = nondep_network_for_plot_no_cranial_nerves, aes(x = fascicle, y=prop_in_mask)) + 
  geom_bar(stat="identity") +
  ggtitle("Proportion of Volume per Fascicle Affected nonDep net 3_09") + 
  ylab("Proportion in Depression Mask") +
  ylim(0,0.4) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(hjust = 0.5))
print(plot_all_fascicles_nondep_network_for_plot_no_cranial_nerves)

@@

sorted_ggplot<-ggplot(data = fascicle_values_dep_sorted_by_overlap, aes(x = fascicle, y=prop_in_mask)) + 
  geom_bar(stat="identity") +
  ylim(0,0.4) +
  xlab("Fascicle") +
  ylab("Proportion Overlap with Depression Mask") +
  ggtitle("Proportion of Volume that Overlaps with Depression Network by Fascicle 3_09")
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(hjust = 0.5, size=30),
        axis.title.x = element_text(size=30),
        axis.title.y = element_text(size=30))
print(sorted_ggplot)

@@

#GET RID OF CRANIAL NERVES
fascicles_alone_rowMeans <- fascicles_alone_rowMeans %>% filter(fascicle %in% fascicle_names_no_cranial_nerves)

@@

sorted_ggplot<-ggplot(data = fascicle_values_sorted_by_overlap, aes(x = fascicle, y=value))+
  ggtitle("Proportion of Volume per Fascicle Affected") + 
  ylab("Proportion") + 
  geom_bar(stat="identity") +
  ylim(0,0.8) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(hjust = 0.5, size=30),
        axis.title.x = element_text(size=30),
        axis.title.y = element_text(size=30))
print(sorted_ggplot)

@@

sorted_ggplot_healthy<-ggplot(data = fascicle_values_sorted_by_overlap, aes(x = fascicle, y=value))+
  ggtitle("Proportion of Volume per Fascicle Affected in Non Depressed") + 
  geom_bar(stat="identity") +
  ylab("Proportion") +
  ylim(0,0.8) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(hjust = 0.5, size=30),
        axis.title.x = element_text(size=30),
        axis.title.y = element_text(size=30))
print(sorted_ggplot_healthy)

# ordered by mean value overall
fascicle_values_sorted_by_overlap$fascicle <- factor(fascicle_values_sorted_by_overlap$fascicle, levels = order_of_mean_values_overall)
sorted_ggplot_healthy_ordered<-ggplot(data = fascicle_values_sorted_by_overlap, aes(x = fascicle, y=value))+
  ggtitle("Proportion of Volume per Fascicle Affected Ordered by mean values NonDepressed") + 
  geom_bar(stat="identity") +
  ylab("Proportion") +
  ylim(0,0.8) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(hjust = 0.5))
print(sorted_ggplot_healthy_ordered)

@@

sorted_ggplot_depressed<-ggplot(data = fascicle_values_sorted_by_overlap, aes(x = fascicle, y=value))+
  ggtitle("Proportion of Volume per Fascicle Affected Depressed") + 
  geom_bar(stat="identity") +
  ylab("Proportion Affected") +
  ylim(0,0.8) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(hjust = 0.5, size=30),
        axis.title.x = element_text(size=30),
        axis.title.y = element_text(size=30))
print(sorted_ggplot_depressed)

# ordered by mean value overall
fascicle_values_sorted_by_overlap$fascicle <- factor(fascicle_values_sorted_by_overlap$fascicle, levels = order_of_mean_values_overall)
sorted_ggplot_depressed_ordered<-ggplot(data = fascicle_values_sorted_by_overlap, aes(x = fascicle, y=value))+
  ggtitle("Proportion of Volume per Fascicle Affected Ordered by mean values Depressed") + 
  ylab("Proportion Affected") +
  geom_bar(stat="identity") +
  ylim(0,0.8) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(hjust = 0.5, size=30),
        axis.title.x = element_text(size=30),
        axis.title.y = element_text(size=30))
print(sorted_ggplot_depressed_ordered)

#no cranial nerves
fascicles_for_plot_no_cranial_nerves <- fascicle_values_sorted_by_overlap[(fascicle_values_sorted_by_overlap$fascicle %in% fascicle_names_dep_network_all_no_cranial_nerves),]

plot_all_fascicles_r_and_l_no_cranial_nerves <-ggplot(data = fascicles_for_plot_no_cranial_nerves, aes(x = fascicle, y=value))+
  ggtitle("Proportion of Volume per Fascicle Affected Net 3_09") + 
  xlab("Fascicle") + 
  ylab("Proportion Affected") +
  geom_bar(stat="identity") +
  ylim(0,0.8) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(hjust = 0.5, size=30),
        axis.title.x = element_text(size=30),
        axis.title.y = element_text(size=30))
print(plot_all_fascicles_r_and_l_no_cranial_nerves )

##### look at mean fascicles affected in dep vs non dep network
######
#plot values within the depression network, and values outside of it

fascicles_dep_25_percent_for_plot <- fascicle_values_sorted_by_overlap[(fascicle_values_sorted_by_overlap$fascicle %in% dep_network_names_top_quartile_preproc),]

plot_all_fascicles_r_and_l_sep_top_quartile <-ggplot(data = fascicles_dep_25_percent_for_plot, aes(x = fascicle, y=value))+
  ggtitle("Proportion of Volume per Fascicle Affected Dep net 3_09, top quartile") + 
  geom_bar(stat="identity") +
  ylab("Proportion") +
  ylim(0,0.8) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(hjust = 0.5))
print(plot_all_fascicles_r_and_l_sep_top_quartile)

#bottom 3 quartiles
fascicles_dep_bottom_3_quartiles_for_plot <- fascicle_values_sorted_by_overlap[(fascicle_values_sorted_by_overlap$fascicle %in% dep_network_bottom_3_quartiles),]

plot_all_fascicles_r_and_l_sep_bottom_3_quartiles <-ggplot(data = fascicles_dep_bottom_3_quartiles_for_plot, aes(x = fascicle, y=value))+
  ggtitle("Proportion of Volume per Fascicle Affected Dep net 3_09, bottom three quartiles") + 
  ylab("Proportion") +
  geom_bar(stat="identity") +
  ylim(0,0.8) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(hjust = 0.5))
print(plot_all_fascicles_r_and_l_sep_bottom_3_quartiles)

#plot values within the depression network, and values outside of it

fascicles_dep_bottom_quartile_for_plot <- fascicle_values_sorted_by_overlap[(fascicle_values_sorted_by_overlap$fascicle %in% dep_network_names_bottom_quartile_preproc),]

plot_all_fascicles_r_and_l_sep_bottom_quartile <-ggplot(data = fascicles_dep_bottom_quartile_for_plot, aes(x = fascicle, y=value)) +
  ggtitle("Proportion of Volume per Fascicle Affected Dep net 3_09, bottom quartile") + 
  ylab("Proportion") +
  geom_bar(stat="identity") +
  ylim(0,0.8) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(hjust = 0.5))
print(plot_all_fascicles_r_and_l_sep_bottom_quartile)

#non dep network
fascicles_nondep_for_plot <- fascicle_values_sorted_by_overlap[(fascicle_values_sorted_by_overlap$fascicle %in% fascicle_names_nondep_network),]

plot_all_fascicles_r_and_l_nondep <-ggplot(data = fascicles_nondep_for_plot, aes(x = fascicle, y=value))+
  ggtitle("Proportion of Volume per Fascicle Affected nonDep net 3_09") + 
  ylab("Proportion") +
  geom_bar(stat="identity") +
  ylim(0,0.8) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(hjust = 0.5))
print(plot_all_fascicles_r_and_l_nondep)

```{r proof_of_concept_unique}

data_empi_acc_f_phq_unique <- data_empi_acc_f_phq %>% 
  group_by(EMPI) %>% 
  arrange(EXAM_DATE) %>% 
  slice(1) %>% 
  ungroup() #n=3737

#have to pull out just the pieces I'm interested in
just_dep_and_empi <- subset(data_empi_acc_f_phq_unique, select = c("EMPI", "depGroupVar"))
added_dep_to_fascicles <- unique(merge(just_dep_and_empi, fascicle_proportions, by = c("EMPI")))

#GET RID OF CRANIAL NERVES
fascicles_alone_rowMeans <- fascicles_alone_rowMeans %>% filter(fascicle %in% fascicle_names_no_cranial_nerves)

sorted_ggplot<-ggplot(data = fascicle_values_sorted_by_overlap, aes(x = fascicle, y=value))+
  ggtitle("Proportion of Volume per Fascicle Affected") + 
  xlab("Fascicle") +
  ylab("Mean Proportion") + 
  geom_bar(stat="identity") +
  ylim(0,0.8) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(hjust = 0.5, size =30),
        axis.title.x = element_text(size=30),
        axis.title.y = element_text(size=30))
print(sorted_ggplot)

#GET RID OF CRANIAL NERVES
fascicles_alone_rowMeans <- fascicles_alone_rowMeans %>% filter(fascicle %in% fascicle_names_no_cranial_nerves)

sorted_ggplot_healthy<-ggplot(data = fascicle_values_sorted_by_overlap, aes(x = fascicle, y=value))+
  ggtitle("Proportion of Volume per Fascicle Affected in Non Depressed") + 
  geom_bar(stat="identity") +
  ylab("Proportion") +
  ylim(0,0.8) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(hjust = 0.5))
print(sorted_ggplot_healthy)

# ordered by mean value overall
fascicle_values_sorted_by_overlap$fascicle <- factor(fascicle_values_sorted_by_overlap$fascicle, levels = order_of_mean_values_overall)
sorted_ggplot_healthy_ordered<-ggplot(data = fascicle_values_sorted_by_overlap, aes(x = fascicle, y=value))+
  ggtitle("Proportion of Volume per Fascicle Affected Ordered by mean values NonDepressed") + 
  geom_bar(stat="identity") +
  ylab("Proportion") +
  ylim(0,0.8) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(hjust = 0.5))
print(sorted_ggplot_healthy_ordered)

#GET RID OF CRANIAL NERVES
fascicles_alone_rowMeans <- fascicles_alone_rowMeans %>% filter(fascicle %in% fascicle_names_no_cranial_nerves)

sorted_ggplot_depressed<-ggplot(data = fascicle_values_sorted_by_overlap, aes(x = fascicle, y=value))+
  ggtitle("Proportion of Volume per Fascicle Affected Depressed") + 
  geom_bar(stat="identity") +
  ylab("Proportion Affected") +
  ylim(0,0.8) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(hjust = 0.5))
print(sorted_ggplot_depressed)

# ordered by mean value overall
fascicle_values_sorted_by_overlap$fascicle <- factor(fascicle_values_sorted_by_overlap$fascicle, levels = order_of_mean_values_overall)
sorted_ggplot_depressed_ordered<-ggplot(data = fascicle_values_sorted_by_overlap, aes(x = fascicle, y=value))+
  ggtitle("Proportion of Volume per Fascicle Affected Ordered by mean values Depressed") + 
  ylab("Proportion Affected") +
  geom_bar(stat="identity") +
  ylim(0,0.8) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(hjust = 0.5))
print(sorted_ggplot_depressed_ordered)

#no cranial nerves
fascicles_for_plot_no_cranial_nerves <- fascicle_values_sorted_by_overlap[(fascicle_values_sorted_by_overlap$fascicle %in% fascicle_names_dep_network_all_no_cranial_nerves),]

plot_all_fascicles_r_and_l_no_cranial_nerves <-ggplot(data = fascicles_for_plot_no_cranial_nerves, aes(x = fascicle, y=value))+
  ggtitle("Proportion of Volume per Fascicle Affected Net 3_09") + 
  ylab("Proportion Affected") +
  geom_bar(stat="identity") +
  ylim(0,0.8) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(hjust = 0.5))
print(plot_all_fascicles_r_and_l_no_cranial_nerves )

##### look at mean fascicles affected in dep vs non dep network
######
#plot values within the depression network, and values outside of it

fascicles_dep_25_percent_for_plot <- fascicle_values_sorted_by_overlap[(fascicle_values_sorted_by_overlap$fascicle %in% dep_network_names_top_quartile_preproc),]

plot_all_fascicles_r_and_l_sep_top_quartile <-ggplot(data = fascicles_dep_25_percent_for_plot, aes(x = fascicle, y=value))+
  ggtitle("Proportion of Volume per Fascicle Affected Dep net 3_09, top quartile") + 
  geom_bar(stat="identity") +
  ylab("Proportion") +
  ylim(0,0.8) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(hjust = 0.5))
print(plot_all_fascicles_r_and_l_sep_top_quartile)

#bottom 3 quartiles
fascicles_dep_bottom_3_quartiles_for_plot <- fascicle_values_sorted_by_overlap[(fascicle_values_sorted_by_overlap$fascicle %in% dep_network_bottom_3_quartiles),]

plot_all_fascicles_r_and_l_sep_bottom_3_quartiles <-ggplot(data = fascicles_dep_bottom_3_quartiles_for_plot, aes(x = fascicle, y=value))+
  ggtitle("Proportion of Volume per Fascicle Affected Dep net 3_09, bottom three quartiles") + 
  ylab("Proportion") +
  geom_bar(stat="identity") +
  ylim(0,0.8) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(hjust = 0.5))
print(plot_all_fascicles_r_and_l_sep_bottom_3_quartiles)

#plot values within the depression network, and values outside of it

fascicles_dep_bottom_quartile_for_plot <- fascicle_values_sorted_by_overlap[(fascicle_values_sorted_by_overlap$fascicle %in% dep_network_names_bottom_quartile_preproc),]
